Import Jaz data

### 2023-12-04 Code/JazDataImport.Rmd
Fixed information extracted from filename column due to new data file path. Generated Emission spectra .Rds

JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = "../")) |>
  separate(col = Filename, into = c("Instrument","Date", "MultiCulti", "Par", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE)

@@

>>>>

JazSpec <- JazSpec %>% 
  mutate(Filename = str_remove(Filename, pattern = "../Data/RawData/MCEmissionSpectra/")) |>
  separate(col = Filename, into = c("Date", "MultiCulti", "Par", "WL"), sep = "([\\/\\/\\_\\_\\_\\_\\_\\_\\.])", remove = FALSE)

@@

```{r remove redundant DF}

remove(JazSpecTrim)
remove(JazSpec)
